---
title: "Final Presentation"
author: "Author: Nicholas Goodman"
date: "`r format(Sys.time(), '%B %d, %Y @ %I:%M %p')`"
output: ioslides_presentation
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

## Packages Used

Tidyverse was used to manipulate data and to plot data.

```{r, echo = TRUE}
library(tidyverse)
```


## NFL Scores and Betting Data

This set was found on Kaggle, and it gives extensive details on every single NFL stadium. It will be used to compare variables between several different stadiums. 

**Variables in the Dataset:**

`stadium_name`: The name of the stadium
`stadium_location`: The location of the stadium
`stadium_open`: The year the stadium opened
`stadium_closed`: The year the stadium closed (if it had closed)
`stadium_type`: The type of stadium (indoor, outdoor, retractable)
`stadium_address`: The address for the stadium

##

`stadium_weather_station_code`: The stadium zip code for weather data collection
`stadium_weather_type`: The weather descriptor for stadium based on average temperature
`stadium_capacity`: The stadium seating capacity
`stadium_surface`: The stadium surface type (grass, turf)
`STATION`: The stadium weather station ID for NOAA data
`NAME`: The stadium weather station name
`LATITUDE`: The stadium latitude.

```{r}

data <- read_csv("nfl_stadiums.csv")
```

##

You only need to have two different graphs, find something interesting in both of them.

```{r}
ggplot(data, aes(x = stadium_type, fill = stadium_year)) + geom_bar() + labs("NFL stadiums that are indoor and outdoor")
```

##

```{r, fig.align = "center", fig.width = 7.5}

```


##

```{r, fig.align = "center", fig.width = 9}

```



##

```{r, fig.align = "center", fig.width = 7, fig.cap = "Figure Caption:"}

```


##

```{r}

```
